Light versus dark in strong-lens galaxies: Dark matter haloes that are rounder than their stars

### 2015-09-08 shapes/paper.tex
Included reply to specific points of criticism in referee report I modified in the paper; Additional small changes to the paper

Recently, \citet{2014MNRAS.445.2181C} introduced a new non-parametric lens tool, \Glass\. Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in lens systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential. In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies. We apply \Glass\ to these lenses to non-parametrically measure the shape and alignment of the stars and {\it dark matter} in these lens galaxies, for the first time. This differs from previous works that have all compared the light distribution with the total mass, rather than the dark matter. Since the stellar component often dominates the central potential, the total mass naturally correlates with the light, potentially masking theoretically interesting results about the dark matter distribution. Our comparison between the stellar and dark matter components is made possible by the fact that \Glass\ uses the stellar mass distribution as a prior on the mass map, ensuring that the dark matter map is always positive.

@@

Lenses are modelled as free-form mass distributions, consisting of mass tiles or pixels. Such lens models are also called non-parametric, which really just means that many more parameters than data constraints are used. Thus the lens models are non-unique, and hence in fact ensembles of these free-form mass distributions are used. From such a mass map, an inertia tensor is defined as
\begin{equation}\label{eq:inertiatensor}
I = 
\begin{pmatrix}
 \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{y} & -\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} \\
-\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} & \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{x}
\end{pmatrix}
\end{equation}
where the sum is over mass pixels, and $M(\boldsymbol{\theta})$ is the mass in a pixel. The eigenvectors of this inertia tensor give the ellipticity axes, and our ellipticity estimator is
\begin{equation}\label{eq:shapeestimate}
    s \equiv 1 - \frac{\lambda_{2}}{\lambda_{1}},
\end{equation}
where $\lambda_{1}$ and $\lambda_{2}$ ($\lambda_{1} \geq \lambda_{2}$) are the eigenvalues. We use this ellipticity estimators to quantify the shapes both of the stellar-mass distribution and of the dark-matter distribution. For the dark matter, only the mass distribution out to the radius of the outermost image is used; for the stellar part, the distribution with within different multiples of $R_e$ (defined as the half-light radius measured with respect to the Petrosian flux) is used. It is necessary to have a cutoff for the regions used to compute the inertia tensor, or else it would be dominated by the outer regions where there is little information. The mass pixels used in this work are at most 4\% of the diameter of the the full mass map. The central region has smaller pixels, to allow for a density cusp at the centre. Each model ensemble had $10^4$ models. Shape and orientation of the distributions are estimated for each of these models, allowing us to constrain the scatter and thus the the statistical uncertainty in these quantities.

The non-parametric mass models themselves are constructed using the \Glass\ framework for modelling multiple-image lenses \citep{2014MNRAS.445.2181C}. \Glass\ produces ensembles of mass maps, each of which reproduces exactly the observed image positions and image parities; also time delays, if measured. The lensing data must be in the form of point images, which could be quasars or simply point-like features in otherwise extended images, but this was not a problem for the lenses studied in this work. The estimated stellar mass (explained below in Section~\ref{sec:data}) is taken as a lower limit on the total mass. The additional mass that needs to be put on top, in order to reproduce the lensing observables, is interpreted as dark matter. \textbf{(Some of that mass may actually be gas, but very little is expected in the early-type galaxies used in this work.) [IS THIS SUPPOSED TO BE IN THERE?]} The criteria of lensing observables and non-negative dark matter by themselves would leave the mass distribution too under-determined. Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the shape shape). The precise formulation of the prior is given in Section~3 of \citet{2014MNRAS.445.2181C}. Tests of how well the shape estimator can be recovered from lensing data are given in Section~5.2 and Figure~8 of that paper.

@@

\begin{table*}
  \begin{center}
    \begin{tabular}{l | l l l l l l l l l}
      Lens & $s_{*}$ & $s_{dm}$ & $\phi$ [^{\circ}] & $e_{*}$ & $e_{dm}$ & $\frac{e_{dm}}{e_{*}}$ & $\frac{e_{dm}}{e_{*}}\mathrm{cos} 2\phi$ & $|\gamma|$ & $\theta_{g}$ [^{\circ}] \\ \hline
      % 0047 & 0.27 & 0.04$\pm$0.02 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.10$\pm$0.07 & 0.07$\pm$0.01 & 120$\pm$5 \\
      % 0414 & 0.19 & 0.06$\pm$0.03 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & 0.20$\pm$0.11 & 0.17$\pm$0.02 & 166$\pm$4 \\
      % 0712 & 0.43 & 0.08$\pm$0.03 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.01 & 141$\pm$3 \\
      % 0911 & 0.22 & 0.07$\pm$0.02 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.27$\pm$0.10 & 0.28$\pm$0.02 & 99$\pm$2 \\
      % 0957 & 0.19 & 0.10$\pm$0.03 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.03 & 159$\pm$8 \\
      % 1115 & 0.30 & 0.11$\pm$0.02 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & 0.08$\pm$0.04 & 0.11$\pm$0.01 & 154$\pm$3 \\
      % 1422 & 0.05 & 0.06$\pm$0.03 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & 0.64$\pm$0.41 & 0.26$\pm$0.01 & 39$\pm$1 \\
      % 1608 & 0.47 & 0.28$\pm$0.01 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.52$\pm$0.03 & 0.19$\pm$0.01 & 145$\pm$2 \\
      % 2016 & 0.47 & 0.12$\pm$0.02 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.20$\pm$0.04 & 0.14$\pm$0.02 & 42$\pm$4 \\
      % 2045 & 0.17 & 0.03$\pm$0.02 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.02 & 23$\pm$7 \\
      % 2237 & 0.24 & 0.05$\pm$0.03 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.21$\pm$0.10 & 0.06$\pm$0.01 & 159$\pm$4 \\
      0047 & 0.27 & 0.04$\pm$0.02 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 & 0.07$\pm$0.00 & 120$\pm$5 \\
      0414 & 0.19 & 0.06$\pm$0.03 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 & 0.17$\pm$0.00 & 166$\pm$4 \\
      0712 & 0.43 & 0.08$\pm$0.03 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.00 & 141$\pm$3 \\
      0911 & 0.22 & 0.07$\pm$0.02 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 & 0.28$\pm$0.00 & 99$\pm$2 \\
      0957 & 0.19 & 0.10$\pm$0.03 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.00 & 159$\pm$8 \\
      1115 & 0.30 & 0.11$\pm$0.02 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 & 0.11$\pm$0.00 & 154$\pm$3 \\
      1422 & 0.05 & 0.06$\pm$0.03 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 & 0.26$\pm$0.00 & 39$\pm$1 \\
      1608 & 0.47 & 0.28$\pm$0.01 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 & 0.19$\pm$0.00 & 145$\pm$2 \\
      2016 & 0.47 & 0.12$\pm$0.02 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 & 0.14$\pm$0.00 & 42$\pm$4 \\
      2045 & 0.17 & 0.03$\pm$0.02 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.00 & 23$\pm$7 \\
      2237 & 0.24 & 0.05$\pm$0.03 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 & 0.06$\pm$0.00 & 159$\pm$4 \\
    \end{tabular}
    \caption[width=\linewidth]{The ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios. The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = \frac{\lambda_1-\lambda_2}{\lambda_1+\lambda_2}$; $\phi$ refers to the misalignment angle between the distributions of luminous and dark matter; $\frac{e_{dm}}{e_{*}}$ denotes the ratio of the dark matter relative to the stellar distribution; $\frac{e_{dm}}{e_{*}}\mathrm{cos} 2\phi$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modelling of the strong lens galaxy.}
    \label{tab:ellipratios}
  \end{center}
\end{table*}

@@

The latter ellipticity definition is commonly used in weak lensing. Especially, it is employed in \citet{2015arXiv150704301S}, a recent study of the shape and alignment of the dark matter halo relative to the distribution of luminous matter. This probe however cannot constrain the $e_{dm}$ directly. Rather, it is sensitive to the ratio $f_{h} = \frac{e_{dm}}{e_{*}}\mathrm{cos} 2\phi$, where $\phi$ is the misalignment angle between the two distributions, and $e_{dm}\mathrm{cos} 2\phi$ is the component of the ellipticity of the dark matter halo projected along the light distribution. In case of perfect alignment and identical shape, $f_{h}$ is equal to 1. In practive however, $f_{h}$ deviates from 1, as among other effects, which cannot be disentangled, misalignment of the two distributions and different shapes affect its value.

@@

\item Three systems have a high stellar ellipticity ($s_* > 0.45$) and correspondingly high alignment between light and dark. One of these -- {\it1608} -- is a known merging pair; we suggest that the other two ({\it0712} and {\it2016}) may also be recent post-merger systems.

@@

\section{Degeneracy between $\theta_{dm}$ and $\theta_{g}$}\label{sec:shearshapedeg}
\begin{figure*}
  \centering
  \includegraphics[width=.9\linewidth]{Figures/theta_scatter.pdf}
  \caption[width=\linewidth]{The two-dimensional distribution of the position angles of the dark matter distribution $\theta_{dm}$ and the direction of the required external shear $\theta_{g}$ of each reconstructed mass distribution of the ensemble of solutions. The panels display this distribution, which traces the degeneracy of the two parameters, for each reconstructed strong lens galaxy in the sample. All the angles are measured north through east.}
  \label{fig:thetascatter}
\end{figure*}

>>>>

Recently, \citet{2014MNRAS.445.2181C} introduced a new non-parametric lens tool, \Glass. Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in lens systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass contributes significantly to the potential. In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies. We apply \Glass\ to these lenses to non-parametrically measure the shape and alignment of the stars and {\it dark matter} in these lens galaxies, for the first time. This differs from previous works that have all compared the light distribution with the total mass, rather than the dark matter. Since the stellar component often dominates the central potential, the total mass naturally correlates with the light, potentially masking theoretically interesting results about the dark matter distribution. Our comparison between the stellar and dark matter components is made possible by the fact that \Glass\ uses the stellar mass distribution as a prior on the mass map, ensuring that the dark matter map is always positive.

@@

Lenses are modelled as free-form mass distributions, consisting of mass tiles or pixels. Such lens models are also called non-parametric, which really just means that many more parameters than data constraints are used. Thus the lens models are non-unique, and hence in fact ensembles of these free-form mass distributions are used. From such a mass map, an inertia tensor is defined as
\begin{equation}\label{eq:inertiatensor}
I = 
\begin{pmatrix}
 \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{y} & -\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} \\
-\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} & \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{x}
\end{pmatrix}
\end{equation}
where the sum is over mass pixels, and $M(\boldsymbol{\theta})$ is the mass in a pixel. The eigenvectors of this inertia tensor give the ellipticity axes, and our ellipticity estimator is
\begin{equation}\label{eq:shapeestimate}
    s \equiv 1 - \frac{\lambda_{2}}{\lambda_{1}},
\end{equation}
where $\lambda_{1}$ and $\lambda_{2}$ ($\lambda_{1} \geq \lambda_{2}$) are the eigenvalues. We use this ellipticity estimators to quantify the shapes both of the stellar-mass distribution and of the dark-matter distribution. For the dark matter, only the mass distribution out to the radius of the outermost image is used; for the stellar part, the distribution with within different multiples of $R_e$ (defined as the half-light radius measured with respect to the Petrosian flux) is used. It is necessary to have a cutoff for the regions used to compute the inertia tensor, or else it would be dominated by the outer regions where there is little information \textbf{[CLAUDIO: Actually, I estimate the shapes for the luminous and dark matter in the same way. I only consider different Petrosian radii in Figure 3, setting different multiples of $R_e$ as a limit for both distributions. Figure 3 gives a sense of how much the estimates change if the distributions are analyzed only within a certain region...]}. The mass pixels used in this work are at most 4\% of the diameter of the the full mass map. The central region has smaller pixels, to allow for a density cusp at the centre.

We estimate the orientation of the distributions of luminous and dark matter by computing the angles $\theta_{*}$ resp. $\theta_{dm}$ of the eigenvector corresponding to the eigenvalue $\lambda_{1}$ ($\lambda_{1} \geq \lambda_{2}$) relative to the x-axis. The misalignment angle $\Delta\theta$ between the distributions is then defined as
\begin{equation}
  \Delta\theta = \theta_{dm} - \theta_{*}.
\end{equation}

Each model ensemble consists of $10^4$ models, for all of which we apply our estimators for the shape and the alignment of the distributions. By identifying the median value and the range 68\% of all the values lie within of this distribution of estimated values, these quantities are constrained and the statistical uncertainties estimated.

The non-parametric mass models themselves are constructed using the \Glass\ framework for modelling multiple-image lenses \citep{2014MNRAS.445.2181C}. \Glass\ produces ensembles of mass maps, each of which reproduces exactly the observed image positions and image parities; also time delays, if measured. The lensing data must be in the form of point images, which could be quasars or simply point-like features in otherwise extended images, but this was not a problem for the lenses studied in this work. The estimated stellar mass (explained below in Section~\ref{sec:data}) is taken as a lower limit on the total mass. The additional mass that needs to be put on top, in order to reproduce the lensing observables, is interpreted as dark matter. \textbf{(Some of that mass may actually be gas, but very little is expected in the early-type galaxies used in this work.) [IS THIS SUPPOSED TO BE IN HERE?]} The criteria of lensing observables and non-negative dark matter by themselves would leave the mass distribution too under-determined. Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the shape shape). The precise formulation of the prior is given in Section~3 of \citet{2014MNRAS.445.2181C}. Tests of how well the shape estimator can be recovered from lensing data are given in Section~5.2 and Figure~8 of that paper.

@@

\begin{table*}
  \begin{center}
    \begin{tabular}{l | l l l l l l l l l}
      Lens & $s_{*}$ & $s_{dm}$ & $\Delta\theta$ [$^{\circ}$] & $e_{*}$ & $e_{dm}$ & $e_{dm}/e_{*}$ & $f_h$ & $|\gamma|$ & $\theta_{g}$ [$^{\circ}$] \\ \hline
      % 0047 & 0.27 & 0.04$\pm$0.02 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.10$\pm$0.07 & 0.07$\pm$0.01 & 120$\pm$5 \\
      % 0414 & 0.19 & 0.06$\pm$0.03 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & 0.20$\pm$0.11 & 0.17$\pm$0.02 & 166$\pm$4 \\
      % 0712 & 0.43 & 0.08$\pm$0.03 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.01 & 141$\pm$3 \\
      % 0911 & 0.22 & 0.07$\pm$0.02 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.27$\pm$0.10 & 0.28$\pm$0.02 & 99$\pm$2 \\
      % 0957 & 0.19 & 0.10$\pm$0.03 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.03 & 159$\pm$8 \\
      % 1115 & 0.30 & 0.11$\pm$0.02 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & 0.08$\pm$0.04 & 0.11$\pm$0.01 & 154$\pm$3 \\
      % 1422 & 0.05 & 0.06$\pm$0.03 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & 0.64$\pm$0.41 & 0.26$\pm$0.01 & 39$\pm$1 \\
      % 1608 & 0.47 & 0.28$\pm$0.01 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.52$\pm$0.03 & 0.19$\pm$0.01 & 145$\pm$2 \\
      % 2016 & 0.47 & 0.12$\pm$0.02 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.20$\pm$0.04 & 0.14$\pm$0.02 & 42$\pm$4 \\
      % 2045 & 0.17 & 0.03$\pm$0.02 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.02 & 23$\pm$7 \\
      % 2237 & 0.24 & 0.05$\pm$0.03 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.21$\pm$0.10 & 0.06$\pm$0.01 & 159$\pm$4 \\
      0047 & 0.27 & 0.04$\pm$0.02 & -41$\pm$33 & 0.15 & 0.02$\pm$0.01 & 0.13$\pm$0.07 & 0.02$\pm$0.15 & 0.07$\pm$0.00 & 120$\pm$5 \\
      0414 & 0.19 & 0.06$\pm$0.03 & 50$\pm$15 & 0.10 & 0.03$\pm$0.01 & 0.30$\pm$0.14 & -0.05$\pm$0.15 & 0.17$\pm$0.00 & 166$\pm$4 \\
      0712 & 0.43 & 0.08$\pm$0.03 & -0$\pm$10 & 0.28 & 0.04$\pm$0.01 & 0.15$\pm$0.05 & 0.15$\pm$0.05 & 0.17$\pm$0.00 & 141$\pm$3 \\
      0911 & 0.22 & 0.07$\pm$0.02 & 25$\pm$14 & 0.12 & 0.04$\pm$0.01 & 0.29$\pm$0.10 & 0.19$\pm$0.12 & 0.28$\pm$0.00 & 99$\pm$2 \\
      0957 & 0.19 & 0.10$\pm$0.03 & 4$\pm$11 & 0.10 & 0.05$\pm$0.01 & 0.49$\pm$0.14 & 0.49$\pm$0.14 & 0.09$\pm$0.00 & 159$\pm$8 \\
      1115 & 0.30 & 0.11$\pm$0.02 & -75$\pm$7 & 0.18 & 0.06$\pm$0.01 & 0.32$\pm$0.07 & -0.28$\pm$0.08 & 0.11$\pm$0.00 & 154$\pm$3 \\
      1422 & 0.05 & 0.06$\pm$0.03 & -51$\pm$18 & 0.03 & 0.03$\pm$0.01 & 1.03$\pm$0.51 & -0.23$\pm$0.65 & 0.26$\pm$0.00 & 39$\pm$1 \\
      1608 & 0.47 & 0.28$\pm$0.01 & -12$\pm$1 & 0.31 & 0.16$\pm$0.01 & 0.53$\pm$0.03 & 0.48$\pm$0.03 & 0.19$\pm$0.00 & 145$\pm$2 \\
      2016 & 0.47 & 0.12$\pm$0.02 & 20$\pm$6 & 0.30 & 0.06$\pm$0.01 & 0.21$\pm$0.04 & 0.16$\pm$0.04 & 0.14$\pm$0.00 & 42$\pm$4 \\
      2045 & 0.17 & 0.03$\pm$0.02 & -4$\pm$20 & 0.09 & 0.02$\pm$0.01 & 0.19$\pm$0.11 & 0.19$\pm$0.11 & 0.11$\pm$0.00 & 23$\pm$7 \\
      2237 & 0.24 & 0.05$\pm$0.03 & -7$\pm$19 & 0.13 & 0.03$\pm$0.01 & 0.21$\pm$0.10 & 0.20$\pm$0.11 & 0.06$\pm$0.00 & 159$\pm$4 \\
    \end{tabular}
    \caption[width=\linewidth]{The ellipticity values of the stellar and dark matter components of the reconstructed strong lens galaxies and their corresponding ratios. The ellipticities $s_{*}$ and $s_{dm}$ are defined by Eq.~\ref{eq:shapeestimate}, while $e_{*}$ and $e_{dm}$ are converted using $e = (\lambda_1-\lambda_2)/(\lambda_1+\lambda_2)$; $\Delta\theta=\theta_{dm}-\theta_{*}$ refers to the misalignment angle between the distributions of luminous and dark matter; $e_{dm}/e_{*}$ denotes the ratio of the dark matter relative to the stellar distribution; $f_h=(e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$ refers to the ratio of the ellipticity component of the dark matter distribution projected along the stellar distribution; $|\gamma|$ and $\theta_{g}$ denote magnitude and direction of the required external shear in the modelling of the strong lens galaxy.} % $e = \frac{\lambda_1-\lambda_2}{\lambda_1+\lambda_2}$
    \label{tab:ellipratios}
  \end{center}
\end{table*}

@@

The latter ellipticity definition is commonly used in weak lensing. Especially, it is employed in \citet{2015arXiv150704301S}, a recent study of the shape and alignment of the dark matter halo relative to the distribution of luminous matter. This probe however cannot constrain the $e_{dm}$ directly. Rather, it is sensitive to the ratio $f_{h} = (e_{dm}/e_{*})\cdot\mathrm{cos} 2\Delta\theta$, where $\Delta\theta$ is the misalignment angle between the two distributions, and $e_{dm}\cdot\mathrm{cos} 2\Delta\theta$ is the component of the ellipticity of the dark matter halo projected along the light distribution. In case of perfect alignment and identical shape, $f_{h}$ is equal to 1. In practive however, $f_{h}$ deviates from 1, as among other effects, which cannot be disentangled, misalignment of the two distributions and different shapes affect its value.

@@

\item Three systems have a high stellar ellipticity ($s_* > 0.45$) and correspondingly high alignment between light and dark. One of these -- {\it1608} -- is a known merging pair; we speculate on the other two lens systems ({\it0712} and {\it2016}) being recent post-merger systems as well.

@@

\section{Degeneracy between $\theta_{dm}$ and $\theta_{g}$}\label{sec:shearshapedeg}
\begin{figure*}
  \centering
  \includegraphics[width=.9\linewidth]{Figures/theta_scatter.pdf}
  \caption[width=\linewidth]{The two-dimensional distribution of the position angles of the dark matter distribution $\theta_{dm}$ and the direction of the required external shear $\theta_{g}$ of each reconstructed mass distribution of the ensemble of solutions. The panels display this distribution, which traces the degeneracy of the two parameters, for each reconstructed strong lens galaxy in the sample. The angles are rotated to be measured north through east here.}
  \label{fig:thetascatter}
\end{figure*}
